The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
Fig. 8

Figure \ref{fig:t_p} shows that $j$ has two different effects on $t_\text{p}$. The most obvious is that when $j$ changes, the location of the boundary between dynamical regimes also changes. This can cause huge spikes in the timescale ratio as that boundary moves close to the initial conditions $(i_0, \Omega_0)$. The other effect is that the timescale ratio becomes small as $j$ increases. We find that the slope for large j is rather consistent, with $t_\text{p}\propto j^{-1} \text{ to } j^{-1.2}$, with the exponent varying slightly with changes to $f$ or $a_\text{b}/r$.

>>>>

Figure \ref{fig:t_p} shows that $j$ has two different effects on $t_\text{p}$. The most obvious is that when $j$ changes, the location of the boundary between dynamical regimes also changes. This can cause huge spikes in the timescale ratio as that boundary moves close to the initial conditions $(i_0, \Omega_0)$. \RR{The bottom panel of Figure \ref{fig:t_p} shows that these spikes correspond to transitions in the family of solution. Separating these families (but not shown) are solutions for which the timescales approach infinity.}
The other effect is that the timescale ratio becomes small as $j$ increases. We find that the slope for large j is rather consistent, with $t_\text{p}\propto j^{-1} \text{ to } j^{-1.2}$, with the exponent varying slightly with changes to $f$ or $a_\text{b}/r$.
